---
title: "An Introduction to Reddit Analysis with rRedditAnalysis"
author: Nan Tang, Jinxin Wang, Lu kang
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{An Introduction to Reddit Analysis with rRedditAnalysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

`rRedditAnalysis` is an R package designed for analyzing Reddit data. This package provides functions to extract threads, summarize discussions, and perform sentiment analysis on subreddit posts.

# Installation

This package can be installed locally from the source.

# Usage

## Extracting Thread Summaries

To get started, you can extract thread summaries using `get_threads_summary()`:

```{r get-threads-summary}
library(rRedditAnalysis)
threads <- get_threads_summary(keyword = "apple")
print(threads)
```

## Analyzing Word Frequencies

You can analyze word frequencies in posts using `user_word_freq()`:

```{r word-freq, eval=FALSE}
# Assuming `threads` is a data frame containing Reddit threads
word_freq <- user_word_freq(username = "Microsoft_Azure", content_type = "comments")
```

## Sentiment Analysis

Performing sentiment analysis on a subreddit's high-frequency terms can be done with `subreddit_highfreq_sentiment()`:

```{r sentiment-analysis, eval=FALSE}
# Perform sentiment analysis on a sample subreddit
sentiment <- subreddit_highfreq_sentiment(keyword = "cat")
```

# Further Details

For more detailed information on each function and its parameters, refer to the function help pages in R:

```{r get-help, eval=FALSE}
# Access help pages for the specific functions
?get_threads_summary
?user_word_freq
?subreddit_highfreq_sentiment
```

# Conclusion

This vignette provided a brief overview of the capabilities of the rRedditAnalysis package. Users are encouraged to review the function documentation and experiment with the package on their own Reddit data for further exploration.
