---
title: "An Introduction to Reddit Analysis with rRedditAnalysis"
author: Nan Tang, Jinxin Wang, Lu kang
date: "`r Sys.Date()`"
output: html_document
vignette: >
  %\VignetteIndexEntry{An Introduction to Reddit Analysis with rRedditAnalysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

`rRedditAnalysis` is an R package with API Wrapper functionality. This package provides tools for Reddit data analysis and visualization, focusing on retrieving user-specific content, threads summary, and sentiment analysis. It can be applied social media analytics and natural language processing.

# Installation
This package can be installed locally from the source.
```{r}
```

# Usage
```{r}
```

## `user_word_freq(username, content_type)`

To call this function, you can input a valid Reddit username and select a content type out of two options: 'comments' and 'submitted' to retrieve the user's content through API.

- For option 'comments', the function will retrieve the most recent 100 comments of the specified user.

- For option 'submitted', the function will retrieve the most recent 100 threads submitted from the specified user.

After API request, it will analyse the requested content and plot a Word Cloud for visualization. Please refer the below examples. 

```{r word-freq, eval=FALSE, warning=FALSE}
# Assuming `threads` is a data frame containing Reddit threads
user_word_freq("Techno_superbowl", "comments")
user_word_freq("Techno_superbowl", "submitted")
```

## Extracting Thread Summaries

To get started, you can extract thread summaries using `get_threads_summary()`:

```{r get-threads-summary}
threads <- get_threads_summary(keyword = "apple")
print(threads)
```



## Sentiment Analysis

Performing sentiment analysis on a subreddit's high-frequency terms can be done with `subreddit_highfreq_sentiment()`:

```{r sentiment-analysis, eval=FALSE}
# Perform sentiment analysis on a sample subreddit
sentiment <- subreddit_highfreq_sentiment(keyword = "cat")
```

# Note
Please do not frequently call each function within one minute, otherwise Reddit API will prevent the user from requesting. If you see error messages like "too many requests" or "request unsuccessful", please wait for at least one minute and try it again. 

# Further Details

For more detailed information on each function and its parameters, refer to the function help pages in R:

```{r get-help, eval=FALSE}
# Access help pages for the specific functions
?get_threads_summary
?user_word_freq
?subreddit_highfreq_sentiment
```

# Conclusion

This vignette provided a brief overview of the capabilities of the rRedditAnalysis package. Users are encouraged to review the function documentation and experiment with the package on their own Reddit data for further exploration.
